Activity Monitoring
========================
load required packages:
```{r}
required <- c('ggplot2','knitr')
lapply(required,require,character.only=TRUE)
```

```{r setoptions, echo=FALSE}
opts_chunk$set(cache=TRUE)
```

Download and read data into R:
```{r}
fileurl <- 'http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip'
if(!file.exists('mon.zip')) {download.file(fileurl, destfile = 'mon.zip')}
downdate <- date()
data <- read.csv(unz('mon.zip','activity.csv'))
```
Data was downloaded from link above on `r downdate`.

##Data Cleaning
```{r}
str(data) #look at data
data$date <- as.Date(as.character(data$date),format='%Y-%m-%d') #convert to Date format
```

##Data Analysis
###Part1
What is mean total number of steps taken per day?  
* Historgram for total number of steps per day  
* Mean and median of total number of steps per day  
```{r}
p1<- ggplot(data=data[data$steps!=0,],aes(x=log(steps)))
p1<- p1+geom_histogram()
p1<- p1+labs(x='log(Number of Steps)',y='Frequency')
p1
outmat <- matrix(nrow=length(unique(data$date)),ncol=2,dimnames = list(as.character(unique(data$date)),c('mean','median')))
mm <- sapply(list('mean','median'),function(x){ tmp<-tapply(data$steps, data$date, x,na.rm=T); outmat[,x]<<- tmp})
outmat
```

###part2
What is the average daily activity pattern?  
* time series plot (interval vs mean number of steps)    
* which time interval contains the maximum number of steps
```{r}
t<-tapply(data$steps,data$interval,mean,na.rm=T)
which.max(t)
df <-data.frame(t) #converting t to dataframe for plotting purposes
df$inv <- as.numeric(rownames(df))
p2 <-ggplot(data=df,aes(x=inv,y=t))
p2<- p2+geom_line()
p2<- p2+labs(x='Interval',y='average number of steps')
p2
```


